Self Referencing Sequences

### 2014-11-05 draft.tex
made conjecture boldface by using begin conj and end conj

\makeatletter
\let\c@lemma=\c@theorem
\let\c@corollary=\c@theorem
\let\c@fact=\c@theorem
\makeatother

\let\realendproof=\endproof
\def\endproof{\hspace*{\fill}$\Box$\realendproof}
\title{Self Referencing Sequences}
\author{Perry Kleinhenz, Fermi Ma and Erik Waingarten}
\date{}							% Activate to display a given date or no date

@@

\begin{conjecture} Any sequence generated by a cycle $C$ is equivalent to any other sequence generated by the same cycle $C$.
\end{conjecture}

@@

\begin{conjecture} If two sequences $\{a_i\}$ and $\{b_i\}$ have elements $a_k \neq b_l$, for $k,l>1$ with the same read distance then they are not equivalent. 
\end{conjecture}

@@

\begin{conjecture} Let $C = (1,2)$. A sequence $s^{(i)}$ is strongly convergent to $s(C, 2)$ if the starting sequence begins with a $2$ and contains no more than 3 elements. A sequence $s^{(i)}$ is strongly convergent to $s(C, 1)$ if the starting sequence begins with a $1$ and contains between 2 and 3 elements. A sequence $s^{(i)}$ is weakly convergent but not strongly convergent to $s(C, a)$ if the starting sequence begins with an $a \in \{1,2\}$ and contains 4 or more elements.
\end{conjecture} 
We make this conjecture on the basis on computer simulations which executes the iterative process to at least 20 iterations. More iterations were not completed because after this point the simulations began to take impractically long amounts of time to complete.

>>>>

%\makeatletter
%\let\c@lemma=\c@theorem
%\let\c@corollary=\c@theorem
%\let\c@fact=\c@theorem
%\makeatother
%
%\let\realendproof=\endproof
%\def\endproof{\hspace*{\fill}$\Box$\realendproof}
\newtheorem{conj}[theorem]{Conjecture} 
\title{Self Referencing Sequences}
\author{Perry Kleinhenz, Fermi Ma and Erik Waingarten}
\date{}							% Activate to display a given date or no date

@@

\begin{conj} Any sequence generated by a cycle $C$ is equivalent to any other sequence generated by the same cycle $C$.
\end{conj}

@@

\begin{conj} If two sequences $\{a_i\}$ and $\{b_i\}$ have elements $a_k \neq b_l$, for $k,l>1$ with the same read distance then they are not equivalent. 
\end{conj}

@@

\begin{conj} Let $C = (1,2)$. A sequence $s^{(i)}$ is strongly convergent to $s(C, 2)$ if the starting sequence begins with a $2$ and contains no more than 3 elements. A sequence $s^{(i)}$ is strongly convergent to $s(C, 1)$ if the starting sequence begins with a $1$ and contains between 2 and 3 elements. A sequence $s^{(i)}$ is weakly convergent but not strongly convergent to $s(C, a)$ if the starting sequence begins with an $a \in \{1,2\}$ and contains 4 or more elements.
\end{conj} 
We make this conjecture on the basis on computer simulations which executes the iterative process to at least 20 iterations. More iterations were not completed because after this point the simulations began to take impractically long amounts of time to complete.
